The LSST DESC 3x2pt Tomography Optimization Challenge

### 2021-03-15 paper/paper.tex
more text

@@

Notably, though, the winning \textsc{funbins} method used the simpler approach desribed above. The success of this simple and fast solution suggests this as an easy heuristic for well-optimized nominal edges, at least
for cases where clustering-like metrics are important.

@@

\section{Full 9-bin results table}
Tables \ref{tab:full_dc2} and \ref{tab:full_buzz} show all calculated metrics when generating nine tomographic 
bins for CosmoDC2 and Buzzard respectively. The \textit{ww} columns
show weak-lensing metrics, \textit{gg} show galaxy clustering, and \textit{3x} the full 3x2pt metric.
Methods above the horizontal line trained bin edges; methods below used fixed fiducial ones, though in some
cases did some hand-tuning of them before submission. In each section the highest scoring method is highlighted.

>>>>

This is not true of the overall winning method for large bin counts - as shown in the tables
in \autoref{app:tables}, significantly more methods acheive a top-scoring spot in the Buzzard
table \ref{tab:full_buzz} than in the CosmoDC2 table \ref{tab:full_dc2}. This reinforces the
conclusions made below in \autoref{sec:train-vs-fix}, though of course the relatively noisy
results make this difficult to interpret.

@@

Notably, though, the winning CosmoDC2 \textsc{funbins} method used the simpler approach desribed above. The 
success of this simple and fast solution suggests this as an easy heuristic for well-optimized nominal edges, 
at least for cases where clustering-like metrics are important.  Its relatively lower
scores on the Buzzard metrics, as noted in \authoref{sec:metric-results}, does however further highlight
the importance of science- and sample-specific training.

@@

\section{Full 9-bin results table} \label{app:tables}
Tables \ref{tab:full_dc2} and \ref{tab:full_buzz} show all calculated metrics when generating nine tomographic 
bins for CosmoDC2 and Buzzard respectively. The \textit{ww} columns
show weak-lensing metrics, \textit{gg} show galaxy clustering, and \textit{3x} the full 3x2pt metric.
Methods above the horizontal line trained bin edges; methods below used fixed fiducial ones, though in some
cases did some hand-tuning of them before submission. In each section the highest scoring method is highlighted.
